---
title: "cofbb"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R package serves the spatial bounding box definitions we use in the Record Lab.

### Requirements

 + [R v4+](https://www.r-project.org/)
 
 + [rlang](https://CRAN.R-project.org/package=rlang)
 
 + [dplyr](https://CRAN.R-project.org/package=dplyr)

### Installation

```
remotes::install_github("BigelowLab/cofbb")
```

### Usage

Retrieve a table of all known bounding boxes.

```{r get_table}
cofbb::get_table()
```

Retrieve one or more regions by name as a table.

```{r get_bb_table}
cofbb::get_bb(c("world", "nwa2"), form = "table")
```

Retrieve one or more regions by name as a list of vector in `[xmin, xmax, ymin, ymax]` order.

```{r get_bb_list}
cofbb::get_bb(c("world", "nwa2"), form = "bb")
```

Or retrieve just one as a vector
```{r get_bb_vector}
cofbb::get_bb("gom", form = "bb")
```

### Ancillary Functions

There are also functions for making `[-180, 180]` <-> `[0,360]` longitude transformations, splitting bounding boxes and determining if a box straddles a particular line of longitude.
